### 2015-11-30 fundamentals/impl.tex
added a footnote about DAGs

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through a
parent-child hierarchy where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a \gls{DAG},
with regions as root nodes and facilities as leaf nodes.

>>>>

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through a
parent-child hierarchy where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a \gls{DAG}\footnote{
\gls{DAG}s are common graph theoretic structures whose most important feature is a 
lack of \emph{cycles}, i.e., there is a single path from the root node to any other 
node in the graph. 
},
with regions as root nodes and facilities as leaf nodes.
